A Data-Driven Framework for Neural Field Modelling

### 2010-11-19 ltx/first_order_framework/LaTeX_Manuscript.tex
small edits to frequency analysis results

As described in Section~\ref{SpectralAnalysisSection}, the basis function configuration can be systematically chosen the account for the full spatial bandwidth from the observations, or alternatively, the configuration can be chosen to represent the neural field up to a specified bandwidth to limit the computational complexity of the estimation procedure. In the examples provided in this paper, the later option was chosen, where the neural field cutoff frequency was further reduced to $\boldsymbol{\nu}_{c\phi} = 0.12$~Hz. The result of the band-limiting effect in the field reconstruction can be seen by comparing Fig.~\ref{fig:Figure4}(A) to Fig.~\ref{fig:Figure4}(B). This effect is due to the spatial frequency response of the basis functions as seen in Fig.~\ref{fig:Figure5}(C). Due to the slow frequency roll-off of Gaussian basis functions an oversampling parameter of $\rho_{\phi} = 1.67$ was chosen. Given the spectral response of the basis functions, the over-sampling parameter, and the spatial domain, an equally spaced grid of $9\times9$ basis functions was used to decompose the field, which resulted in $81$ states. %The other parameter of the basis functions, $\sigma_{\phi}^2$, was set based on equation \ref{eq:CutoffFromBasisFuncWidth} and the chosen neural field bandwidth $\boldsymbol{\nu}_{c\phi}$, to give $\sigma_{\phi}^2=2.5$.

>>>>

As described in Section~\ref{SpectralAnalysisSection}, the basis function configuration can be systematically chosen the account for the full spatial bandwidth from the observations, or alternatively, the configuration can be chosen to represent the neural field up to a specified bandwidth to limit the computational complexity of the estimation procedure. In the examples provided in this paper, the later option was chosen, where the neural field cutoff frequency was further reduced to $\boldsymbol{\nu}_{c\phi} = 0.12$~Hz. The band-limiting effect on the field reconstruction can be seen by comparing Fig.~\ref{fig:Figure4}(A) to Fig.~\ref{fig:Figure4}(B). This effect is due to the spatial frequency response of the basis functions, which is shown in Fig.~\ref{fig:Figure5}(C). Due to the slow roll-off in the frequency response of Gaussian basis functions an oversampling parameter of $\rho_{\phi} = 1.67$ was chosen. Given the spectral response of the basis functions, the over-sampling parameter, and the spatial domain an equally spaced grid of $9\times9$ basis functions was used to decompose the field, which resulted in $81$ states. %The other parameter of the basis functions, $\sigma_{\phi}^2$, was set based on equation \ref{eq:CutoffFromBasisFuncWidth} and the chosen neural field bandwidth $\boldsymbol{\nu}_{c\phi}$, to give $\sigma_{\phi}^2=2.5$.
